Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-06 doc/report/design.tex
update texts in some section, now turn back to coding and presentation preparation

The dotted lines show some existing approaches that seek to provide access to physical objects through gateways from the broader Internet. In our project, we focus on the solid lines where the users can interact with them directly. Also as has been pointed out in the requirements, the fall-back scheme for complicated tasks are enabled by the communication between the glasses and the gateway. Though simple enough, we find it essentially useful to have this architectural figure in mind when considering users' interaction.

>>>>

The dotted lines show some existing (even gradually commercialized) approaches that seek to provide access to physical objects through gateways from the broader Internet. In our project, we focus on the solid lines where the users can interact with them directly. Also as has been pointed out in the requirements, the fall-back scheme for complicated tasks are enabled by the communication between the glasses and the gateway. Though simple enough, we find it essentially useful to have this architectural figure in mind when considering users' interaction.

### 2013-05-06 doc/report/implementation.tex
updating texts for design section. changed intro due to new template reference problem. A grammar error in implementation.tex
update texts in some section, now turn back to coding and presentation preparation

In this section, we details our implementation on Arduino \cite{Arduino} platform. The whole system is comprised of a glass module, numbers of clients, and a gateway. We will start by the clients, which responds to different message sent by others. The complexity of coordination is pushed to the glass, and only minimal function are provided in the gateway.

\subsection{Clients}
The clients are comprised of a main Arduino board, an IR receiver, an XBee radio, and various actuators. In our current system, we have a relay which can control the AC power plug, and we have a USB connected computer to control video playing.

The main function of client is to respond IR signal, and communicate with glass to receive corresponding commands. When there is no glass initiating connection, the client simply lives in {\it IDLE} mode; while when they receive IR signal, indicating the user is expressing interest in interacting with it, the client responds with an XBee acknowledgement and goes into {\it PENDING} state. In this case, since the client doesn't know how many other clients have also responded to the glass, it will wait until a connection signal. If there are multiple clients waiting to be verified, the glass will coordinate all of them by sending the right verifying message. The active client that is being verified will blink faster, as visual feedback to users. When it receives the connection message, it goes to {\it CONNECTED} state and is ready to take commands. To summarize the behavior, we have a state machine in Fig.\,\ref{fig:clientFSM} for illustration.

@@

Within {\it CONNECTED} state, the clients' behaviors are different from each other according to the device it is connected to. In our prototype, we have two different types of devices. The first is a relay, which can then control the whole AC power supply. To control the relay, we only need to set a digital pin to {\it LOW} or {\it HIGH}, and each action is encoded in the command set from the glass. The second is a computer that is used to play video. And the direct interaction includes adjusting the volume and pause/play. These commands are sent to the computer through USB serial data.

>>>>

In this section, we detail our implementation on Arduino \cite{Arduino} platform. The whole system is comprised of a glass module, numbers of clients, and a gateway, as shown in the architecture figure (Fig.\,\ref{fig:sysarch}) in last section. We will start from the clients, whose primary tasks are to interface between the Glass and the devices that are attached to it. Then we move on to the implementation of the Glass, who manges users' gesture recognition and communication with clients. The functionality in gateway so far is only minimum to communicate with clients, since it's not the primary focus of this project.

\subsection{Clients}
The clients are comprised of a main Arduino board, an IR receiver, an XBee radio, and various actuators. We used Arduino Uno, which has an ATmega328 microcontroller and suffice our purpose in this project. We use off-the-shell IR receivers ({\color{red} confirm it is PNA4602}), which outputs 0V (low) on detection of 38 KHz carrier or 5V (high) otherwise. The XBee radio, accompanied with an XBee modems, takes charge of the communication with the Glass. Additional components are subject to the device being attached to. In our current system, we have a relay ({\color{red} need to know relay model}) which can control the AC power plug, and we have a USB connected computer to control video playing.

The main function of the client is to respond IR signal, and communicate with the Glass to receive corresponding commands. Normally, the client lives in {\it IDLE} mode. When they receive IR signals, indicating the user is expressing interest in interacting with it, the client responds with an XBee acknowledgement and goes into {\it PENDING} state. In this case, since the client doesn't know how many other clients have also responded to the glass, it will wait until a connection signal. If there are multiple clients waiting to be verified by the Glass, the coordination is done at the Glass through sending the right verifying message. To provide visual feedback to the user, the active client that is being verified will blink faster. When it receives the connecting message, it goes to {\it CONNECTED} state and is now ready to take commands. To summarize the clients' behavior, we have a state machine in Fig.\,\ref{fig:clientFSM} for illustration.

@@

Within {\it CONNECTED} state, the clients will react differently according to the device it is connected to. In our prototype, we have two different types of devices. The first is a relay, which can control the whole AC power supply. The interface to relay is simply an digital pin. We only need to set it to {\it LOW} or {\it HIGH}. Such command is transmitted remotely from the Glass through XBee using encoded packet. The second tyep is a computer that is used to play video. To send command to the computer, we have a USB adaptor and a python script taking charge of the translation. We use {\it pyserial} and {\it appscript} in the software. And this enables controlling the play and pause of an video, and system-wide volume control.

{\color{red} I arrived here for the second pass - Ben}
